\documentclass[12pt]{article}
\usepackage{pictex,amsmath,amssymb,amsbsy,amsfonts}
\usepackage{graphics,graphicx}
\usepackage{mathabx}

\setlength{\voffset}{-0.25in}
\setlength{\headsep}{+0.5in}
\setlength{\parskip}{1em}
\setlength{\parindent}{0em}

\def\vu{\mathbf{u}}
\def\vv{\mathbf{v}}
\def\vb{\mathbf{b}}
\def\vs{\mathbf{s}}
\def\vw{\mathbf{w}}

\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{mdframed}
\usepackage[utf8]{vietnam}



\usepackage{listings}
\definecolor{vgreen}{RGB}{104,180,104}
\definecolor{vblue}{RGB}{49,49,255}
\definecolor{vorange}{RGB}{255,143,102}

\lstdefinestyle{verilog-style}
{
    language=Verilog,
    basicstyle=\small\ttfamily,
    keywordstyle=\color{vblue},
    identifierstyle=\color{black},
    commentstyle=\color{vgreen},
    numbers=left,
    numberstyle=\tiny\color{black},
    numbersep=10pt,
    tabsize=8,
    moredelim=*[s][\colorIndex]{[}{]},
    literate=*{:}{:}1
}

\makeatletter
\newcommand*\@lbracket{[}
\newcommand*\@rbracket{]}
\newcommand*\@colon{:}
\newcommand*\colorIndex{%
    \edef\@temp{\the\lst@token}%
    \ifx\@temp\@lbracket \color{black}%
    \else\ifx\@temp\@rbracket \color{black}%
    \else\ifx\@temp\@colon \color{black}%
    \else \color{vorange}%
    \fi\fi\fi
}
\makeatother

\usepackage{trace}


\newmdenv[linecolor=blue,skipabove=\topsep,skipbelow=\topsep,leftmargin=5pt,rightmargin=-5pt,innerleftmargin=5pt,innerrightmargin=5pt]{mybox}


\begin{document}
\section{Combinational Logic circuit and Sequential Logic circuit}
\begin{enumerate}
    %1
    \item Combinational Logic Circuit: \\
    \begin{itemize}
        \item Combinational Logic Circuit is the circuit made up from the basic \textbf{logic} gate (AND, OR, NOT) or universal gates (NAND, NOR).  
        \item These gates are \textbf{combined} together to produced more complicated circuits.
        \item Output of the Combinational Circuit depend totally in the current input.
    \end{itemize}
    %2
    \item Sequential Digital Circuit: \\
    \begin{itemize}
        \item The inputs of Sequential Circuit also include the previous output from the circuit. 
        \item In Sequential Circuit, memory elements is used to store the previous value of the last output of the circuit. 
        \item Output depend on both circuit state and current input.
    \end{itemize}
\end{enumerate}
\section{Question 2: }
\begin{enumerate}
    %1
    \item How can you declare a negative triggered edge in sensitive list ? \\
    \begin{lstlisting}[style={verilog-style}]
        module Edge_trigger
        always @(negedge clk) begin
            //Statement:
        end
    \end{lstlisting}
    %2
    \item In the example 6, assume that out1 = 5 and out2 = 0, in = 1. What is the value of out1 and out2 in the clock trigger? Explain your results? \\
     \begin{itemize}
        \item The value of out1 is 0 and out2 is 5.
        \item Because when initial rst = 0, when we get the out1 and out2, rst = 1. When trigger the clock trigger, out1 and out2 will equal 0 and the circuit will be performed in sensitive list, in = 1 will perform the \textbf{else if} statement the later out1 is assigned to initial out2 and the later out2 is assigned to the initial out1.
     \end{itemize} 
\end{enumerate}

\end{document}